% This file contains the text portion of the Cost Proposal portion of the project charter

As the CSE team for the Autonomous Drone Project, most of our tasks delegated are in relation to the drone's build, and building software to get it to perform its necessary tasks. Taking into account money from sponsorship, our approximate budget is \$1600. The drone build cost estimate is based on insight from our professor who is gathering the parts. The drone must be acquired in order to participate in the competition. A student must become FAA certified as a requirement for the competition. The drone build cost will be covered through a variety of department funds. The FAA certification will be covered by the budget afforded by Raytheon. Major expenses of the drone build include ordering a single board computer, ordering a microcontroller, and a GPS module to be fitted to the drone.

% 9.1 PRELIMINARY BUDGET
\newpage
\subsection{Preliminary Budget}
In addition to the parts below, FAA Pilot Certifications will be required. Two certifications (\$175 each) will be acquired for a total of \$350.

% For tables in LaTeX, see: https://www.overleaf.com/learn/latex/Tables
\begin{table}[h]
    \resizebox{\textwidth}{!}{
        \begin{tabular}{|l|l|l|l|}
            \hline
            \textbf{Part Type} & \textbf{Price} & \textbf{Quantity} & \textbf{Total Cost} \\ \hline
            Companion Computer & \$185 & 1 & \$185 \\ \hline
            Microcontroller & \$485.99 & 1 & \$485.99 \\ \hline
            Brushless Motor Set (4PCS) & \$40-\$50 & 1 & \$40-\$50 \\ \hline
            Electronic Speed Control Set (4PCS) & \$40-\$50 & 1 & \$40-\$50 \\ \hline
            GPS and RTK & \$325 & 1 & \$325 \\ \hline
            Camera & \$25 & 1 & \$25 \\ \hline
            Propeller Set & \$15-\$20 & 1 & \$15-\$20 \\ \hline
            Battery & TBD & 1 & TBD \\ \hline
            Radio Receiver & \$20-\$30 & 1 & \$20-\$30 \\ \hline
            Telemetry & \$96 & 1 & \$96 \\ \hline
            LIDAR Distance Sensor & \$30 & 1 & \$30 \\ \hline
            Radio Transmitter & \$130-\$160 & 1 & \$130-\$160 \\ \hline
            Brushless Camera Gimbal & \$50-\$60 & 1 & \$50-\$60 \\ \hline
            Optical Flow Sensor & \$20-\$30 & 1 & \$20-\$30 \\ \hline
            ACE Combat System & \$39.95 & 1 & \$39.95 \\ \hline
        \end{tabular}}
    \caption{An overview of the project's components and their prices}
\end{table}

% 9.2 CURRENT & PENDING SUPPORT
\subsection{Current \& Pending Support}
\begin{itemize}
    \item \$5,000 will be provided by Raytheon Technologies
    \item \$800 will be provided by the University of Texas at Arlington
    \item The CSE department may provide additional funding.
\end{itemize}
